CP_MSSA

### 2025-03-10 Code/R/Research/CP_MSSA.Rmd
Exp case snr fix

## 4
# A <- exp(ones %o% c(-rep(0.05, 9)) * 1:N)
# w <- rep(1 / 12, 9)
# phi <- ones %o% rep(0, 9)
# save_file_name <- "same_exp_same_freq"
# groups_mssa <- list(1:2)
# groups3 <- list(1)
# groups_cp <- list(1:2)

## 5
A <- exp(ones %o% c(-rep(0.05, 7), -0.03, -0.03) * 1:N)
w <- rep(1 / 12, 9)
phi <- ones %o% rep(0, 9)
save_file_name <- "diff_exp_same_freq"
groups_mssa <- list(1:4)
groups3 <- list(1:2)
# groups_cp <- list(1:4)
groups_cp <- list(1:2)

@@

all_mv_rmse_res <- all_mv_rmse(R)
save(
  L_mssa,
  L_cp,
  L_ho,
  groups_mssa,
  groups_cp,
  groups3,
  all_mv_rmse_res,
  file = paste0(
    "./Research/comp_results/all_",
    save_file_name,
    "_mv_comp.RData"
  )
)
print(all_mv_rmse_res)
```

>>>>

## 4
# A <- 20 * exp(ones %o% c(-rep(0.05, 9)) * 1:N)
# w <- rep(1 / 12, 9)
# phi <- ones %o% rep(0, 9)
# save_file_name <- "same_exp_same_freq"
# groups_mssa <- list(1:2)
# groups3 <- list(1)
# groups_cp <- list(1:2)

## 5
A <- 20 * exp(ones %o% c(rep(0.05, 7), 0.03, 0.03) * 1:N)
w <- rep(1 / 12, 9)
phi <- ones %o% rep(0, 9)
save_file_name <- "diff_exp_same_freq"
groups_mssa <- list(1:4)
groups3 <- list(1:2)
groups_cp <- list(1:4)

@@

all_mv_rmse_res <- all_mv_rmse(R)
save(
  L_mssa,
  L_cp,
  L_ho,
  groups_mssa,
  groups_cp,
  groups3,
  all_mv_rmse_res,
  sd,
  file = paste0(
    "./Research/comp_results/all_",
    save_file_name,
    "_mv_comp.RData"
  )
)
print(all_mv_rmse_res)
```
